\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-06 doc/paper.tex
doc/paper.tex: differentiate between inheritance and component separation

The large variety of supersymmetric models and potential
investigations makes it likely that the user wants to modify the
generated spectrum generator source code or reuse components in
further programs.  \fs offers two levels to influence the code: (i) On
the \mathematica model file level the model itself or GUT/weak scale
boundary conditions as well as input and output parameters can be
controlled (see \secref{sec:quick-start-alternative-models} and
\secref{sec:adapting-model-files} for examples).  (ii) In particular
\fs uses C++ object orientation features to modularize the source code
in order to make it easy for the user to modify, reuse, replace or
extend the individual components (see \secref{sec:adapting-cpp-code}
for examples).  An important application of this concept are the
boundary conditions, for which the C++ level offers a wider range of
possibilities.  The boundary conditions solver provides a plugin
mechanism via a common \code{Constraint} interface, which allows a
user to exchange or add boundary conditions at any scale.  An
elaborate example of a tower of effective field theories and multiple
matching scales is presented in \secref{sec:tower construction}.
Alternatively, the modular structure makes it straightforward to take
\fs generated code for e.g.\ RGEs or self-energies and reuse it in an
existing code for some other purpose.  Conversely, it is also easy to
include code from elsewhere into the spectrum generator.  For an
example see \secref{sec:integrating-custom-built}.

>>>>

The large variety of supersymmetric models and potential
investigations makes it likely that the user wants to modify the
generated spectrum generator source code or reuse components in
further programs.  \fs offers two levels to influence the code: (i) On
the \mathematica model file level the model itself or GUT/weak scale
boundary conditions as well as input and output parameters can be
controlled (see \secref{sec:quick-start-alternative-models} and
\secref{sec:adapting-model-files} for examples).  (ii) In particular
\fs uses C++ object orientation features to modularize the source code
so that it is sharply divided into manifestly separate building blocks.
This modular architecture makes it easy
for the user to modify, reuse, replace or
extend the individual components (see \secref{sec:adapting-cpp-code}
for examples).  An important application of this concept are the
boundary conditions, for which the C++ level offers a wider range of
possibilities.  The boundary conditions solver provides a plugin
mechanism via a common \code{Constraint} interface, which allows a
user to exchange or add boundary conditions at any scale.
To realized this, all (derived) constraint objects are intentionally
kept outside the solver.  Despite being independent of one another,
they can fit together with the aid of class inheritance.  An
elaborate example of a tower of effective field theories and multiple
matching scales is presented in \secref{sec:tower construction}.
Alternatively, the modular structure makes it straightforward to take
\fs generated code for e.g.\ RGEs or self-energies and reuse it in an
existing code for some other purpose.  Conversely, it is also easy to
include code from elsewhere into the spectrum generator.  For an
example see \secref{sec:integrating-custom-built}.
